Dissecting the causal question underlying the association between cancer and ADRD 

### 2021-03-31 04_reports/manuscript.Rmd
added ideas from melodem abstract, still rough but clearer aim (I hope)

@@

To match the analysis to our initial question, we considered as inclusion criteria being between 60 and 70 years old at study entry, without history of cancer diagnosis, free of cognitive decline or with previous history of dementia. Out of 7983 persons who participated at baseline, `r total_n` were considered eligible. Time to cancer diagnosis, to dementia diagnosis and death status was measured for all participants. All participants were followed from study entry until dementia diagnosis, death or 20 years after their individual baseline date, whichever ocurred first.

@@

@@

>>>>

Bias cannot be defined or assessed if the causal question is not explicitly specified. To define the underlying causal question there are two core challenges. First, specifying cancer diagnosis as the proxy for an underlying biological mechanism we would ideally intervene upon.

Second, to rely on the independent censoring assumption in regards to the competing event of death when the inrestes is on the direct effect of cancer in dementia risk.

With these considerations in mind, and illustrated through directed acyclic graphs, we describe a case study using data from the Rotterdam Study, a population-based prospective cohort with over 20 years of follow up. Through this case study we describe how can we connect the causal question to the analytic decisions with real-world data and demonstrate how point estimates may vary substantially depending on the assumptions related to previous points.

How information on mortality and cause of death can provides insight about the direction of some sources of bias.

@@

To match the analysis to our initial question, we considered as inclusion criteria being between 60 and 70 years old at study entry, without history of cancer diagnosis, free of cognitive decline or with previous history of dementia. Out of 7983 persons who participated at baseline, `r total_n` were considered eligible. Time to cancer diagnosis, to dementia diagnosis and death status was measured for all participants. All participants were followed from study entry until dementia diagnosis, death or 20 years after their individual baseline date, whichever occurred first.

@@

We begin illustrating the most simple scenario (as Figure 1), were Pin1 overexpression is defined as "ever vs. never" and we consider death as an independent censoring mechanism. We consider baseline covariates for adjustment such as age at study entry, sex, educational attainment, smoking status, alcohol intake status.

@@

Make a table of definition of weights based on cancer def. and
